### 2009-05-05 doc/tech_doc/jura/jura-tech-doc.tex
Documenting JURA

\begin{figure}[ht]
\centering{{{\includegraphics[width=0.9\textwidth]{components.pdf}}}
\caption{\label{fig:components}Components participating in accounting.} }
\end{figure}

@@

The command line format is a subset of that of logger:

@@

\subsection{Parsing job log files}
\label{joblogs}
The job log files generated by A-REX reside under the directory
\textit{<control\_dir>/logs}. They have file name format
\textit{<ngjobid>.<random>}, where \textit{ngjobid} is the identifier
created for the job by A-REX, \textit{random} is a randomly generated
sequence of alphanumeric characters to avoid collision of different
files pertaining to the same job. For each job and for each reporting
destination (i.e. accounting service to be contacted), at least two
log files are written for each job: one at the time of job submission,
and another one after the job finishes, and possibly others at each
start and stop event.

@@

\subsection{Accessing LUTS}
After the necessary URs to be inserted are filled and valid, they are
submitted to the accounting service through its insertion
interface. The service in particular, SGAS LUTS has a simple custom
web service interface loosely based on WS-ResourceProperties.

To increase communication efficiency, LUTS accepts a batch of several
URs within a single request. The batch is an XML element called
\textit{UsageRecords}, containing elements representing URs. The
maximal number of URs in a batch is limited, it can be set in the
``\textit{jobreport\_options=}'' line of the A-REX configuration file
(see Appendix \ref{config}).

@@

The authentication towards the SGAS LUTS is done via the standard
X.509 certificate mechanism over SSL protocol: a chain of valid
(i.e. not expired and/or revoked) certificates with a trusted root
certification authority is accepted as authentic identification of the
client. This means that the client can access the service using a
proxy certificate as well. In the scenario involving A-REX and JURA,
all usage records are submitted using credentials given in the
\textit{jobreport\_credentials} line of the A-REX configuration file
(see Appendix \ref{config}), and no proxies are used. Normally the
credentials for the A-REX service should be used.

@@

\section{Implementation}
JURA is written merely in C++, and is tested in a GNU/Linux
environment, built with standard GNU tools. It depends on the HED
libraries, and thus also on all mandatory dependencies thereof. The
\textit{openssl} library is also required, since sensitive accounting
data needs to be sent in a secure manner.

%TODO about other service types

When deployed, the executable called ``\textit{jura}'' is placed into the
\textit{libexec} directory of the ARC install location. There is a
symbolic link %TODO make it so!
to the executable in the same directory, called ``\textit{logger}'',
through which A-REX executes JURA. This is to keep compatibility with
the old logger client. No other executables or wrapper scripts are
needed.

@@

%   loggerurl: jobreport, JSDL

%   (lifetime)

%   jobreport

%   accounting\_options: jobreport\_options

%   key\_path, certificate\_path, ca\_certificates\_dir: jobreport\_credentials

\section{Usage Record properties}
\label{log2ur}
%   input file format

%   filled properties

%   missing properties

>>>>

\begin{figure}[ht]
\centering{{{\includegraphics[width=0.9\textwidth]{components.pdf}}}
\caption{\label{fig:components}The usage reporting mechanism.} }
\end{figure}

@@

The command line format is a subset of that of logger: %TODO make it so!

@@

\subsection{Parsing job log files}
\label{joblogs}
The job log files generated by A-REX reside under the directory
\textit{<control\_dir>/logs}. They have file name format
\textit{<ngjobid>.<random>}, where \textit{ngjobid} is the identifier
created for the job by A-REX, \textit{random} is a randomly generated
sequence of alphanumeric characters to avoid collision of different
files pertaining to the same job. For each job and for each reporting
destination (i.e. accounting service to be contacted), at least two
log files are written for each job: one at the time of job submission,
and another one after the job finishes, and possibly others at each
start and stop event. Reporting destination URLs are acquired from
``\textit{jobreport=}'' lines in the A-REX configuration file, and a
limited number of additional destinations can be supplied by the
submitter in the job description.

@@

\subsection{Accessing LUTS}
\label{accessing}
After the necessary URs to be inserted are filled and valid, they are
submitted to the accounting service specified by the URL in the
``\textit{loggerurl=}'' line of the job log file, through the
insertion interface of the service. The service in particular, SGAS
LUTS has a simple custom web service interface loosely based on
WS-ResourceProperties\cite{wsrp}.

To increase communication efficiency, LUTS accepts a batch of several
URs within a single request. The batch is an XML element called
\textit{UsageRecords}, containing elements representing URs. The
maximal number of URs in a batch is limited, it can be set in the
``\textit{jobreport\_options=}'' line of the A-REX configuration file
(see Sec. \ref{config}).

@@

The authentication towards the SGAS LUTS is done via the standard
X.509 certificate mechanism over SSL protocol: a chain of valid
(i.e. not expired and/or revoked) certificates with a trusted root
certification authority is accepted as authentic identification of the
client. This means that the client can access the service using a
proxy certificate as well. In the scenario involving A-REX and JURA,
all usage records are submitted using credentials given in the
\textit{jobreport\_credentials} line of the A-REX configuration file
(see A-REX Description and Administration Manual\cite{arex}), and no
proxies are used. Normally the credentials for the A-REX service
should be used.

@@

JURA can ne set up through the configuration file of A-REX. Three
commands are used by JURA: \textit{jobreport},
\textit{jobreport\_credentials} and \textit{jobreport\_options}. See the
A-REX Description and Administrator's Manual\cite{arex}, Section
``Configuration'' for details.

The \textit{jobreport\_options} command allows passing a generic option
string to JURA verbatim. This option can be used for example for
service-related settings. Currently only SGAS LUTS service is
supported, for which the UR batch size can be set with the following
command format:

\verb|jobreport_options="urbatch:size"|

%TODO implement!
where \textit{size} is a positive integer, the number of URs sent
within one request. If not given, the default is 50.

\section{Implementation}
JURA is written merely in C++, built with standard GNU tools, and
tested in a GNU/Linux environment. It depends on the HED libraries,
and thus also on all mandatory dependencies thereof. The
\textit{openssl} library is also required, since sensitive accounting
data needs to be sent in a secure manner.

%TODO enable other service types, write about them

\section{Installation and deployment}

Upon \verb|make install|, the executable called ``\textit{jura}'' is
placed into the \textit{libexec} directory of the configured ARC
install location. There is a symbolic link %TODO make it so!
to the executable in the same directory, called ``\textit{logger}'',
through which A-REX executes JURA. This is to keep compatibility with
the old logger client. No other executables or wrapper scripts are
installed.

\section{Limitations and issues}
Although stable, JURA still has minor imperfections, some of them
stemming from flaws in A-REX or the \textit{arcsub} client:

\begin{itemize}
\item The time frequency of running JURA is not configurable. It is a
  hardcoded value in A-REX: 3600 seconds, i.e. one hour. 
\item The number of user-supplied reporting destinations is limited
  for the sake of robustness. This upper limit is hardcoded: max. 3
  destinations are parsed from JSDL, and max. 1 from RSL.
\item The \textit{arcsub} job submission client removes all but one
  reporting destination URL from the job description, further limiting
  the number of user-supplied destinations.
\item The expiration time of job log files can be given in each
  ``\textit{jobreport=}'' line in the configuration file. However,
  only one single value is used for all reporting destinations; the
  last one given overrides the previous ones.
\item Missing UR properties: charge, processors, network etc. see
  App. \ref{log2ur}
\item The GNU time memory measurement bug
\end{itemize}

@@

\section{Usage Record properties}
\label{log2ur}
The following table shows which properties in OGF UR are filled, what
data source was used for them, which properties are missing, and what
extensions have been added to UR.

\begin{tabular}{|p{0.2\columnwidth}|p{0.5\columnwidth}|p{0.2\columnwidth}|}
\hline
\textbf{UR Property}&
\textbf{Description}&
\textbf{Source\newline(job log entry)}\\
\hline\hline
RecordId&
Globally unique identifier for UR&
nodename,\newline
ngjobid\\
\hline
GlobalJobId&
Globally unique identifier of job&
globalid\\
\hline
LocalJobId&
CE-specific identifier of job&
localid\\
\end{tabular}

%  filled:
% RecordId: nodename+ngjobid
% GlobalJobId: globalid
% LocalJobId: localid
% GlobalUserName: usersn
% LocalUserId: localuser
% JobName: jobname
% Status: status
% WallDuration: usedwalltime
% CpuDuration: usedcputime
% StartTime: submissiontime (?)
% EndTime: endtime
% MachineName: nodename/1
% Host: nodename
% SubmitHost: clienthost
% Queue: lrms
% ProjectName: projectname

%  unfilled:
% ProcessId (localjobid?)
% Charge

%  extra:
% UserVO(?) userproxy
% RuntimeEnvironment: runtimeenvironment

\section{Additional job log file entries}
Table \ref{table:joblog} describes entries of the job log file not
present in Table \ref{table:ur}.
